%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
%\addbibresource{bibliography.bib}
\usepackage[spanish]{babel}

\usepackage[utf8x]{inputenc}

\begin{document}
\header{Carlos }{L\'{o}pez Roa}
       {Technologist, Entrepreneur, Data Scientist}


% In the aside, each new line forces a line break
\begin{aside}
  \section{contact}
   % \textbf{Tel: } 442-212-35-88
    \textbf{Mobile:} +33 060 
    		          568 1556
    \href{mailto:me@mr3m.me}{me@mr3m.me}
    \href{https://github.com/mr3m}{Github : mr3m}
  \section{languages}
    Spanish / Native
    English / TOEFL
    German / A1
  \section{programming}
    %{\color{red} $\varheartsuit$} 
    C, R
    Java, Python
    Shell-Bash
    SQL, XML
    CSS3 \& HTML5
    JavaScript
    Matlab
    Mathematica
     \LaTeX{}, B\textsc{ib}\TeX{}
   \section{mathematical expertise}  
   Complex \& real analysis
   Linear algebra
   Analytical geometry
   Multivariable calculus
   Superior algebra
   Ordinary \& Partial Differential Equations
   Statistics \& Probability
   Functional analysis
   Finite element analysis
   Wavelet Analysis
   Dynamical Systems
   Neural networks design 
\end{aside}

\section{interests}

Data mining, Mathematical modeling, Big Data analytics, Computer simulation, Cloud computing, Internet of things, Sensorgrid, Artificial Intelligence, Machine Learning, Web Crawling, Embedded systems

\section{education}

\begin{entrylist}
\entry
{09/15-08/17}
{M.Sc. \href{http://www.em-dmkm.eu/}
             {\normalfont{Data Mining and Knowledge Management}}}
     {\href{http://www.univ-lyon2.fr/}{Universite Lumiere Lyon 2}, Lyon, Fra}
     {%\href{https://dl.dropboxusercontent.com/u/2115508/Tesis.pdf
}
\entry
{10/09-04/14}
{B.Sc. \href{http://www.fata.unam.mx/tecnologia}
             {\normalfont{Technology}}}
  {\href{http://www.fata.unam.mx/}{Center of applied Physics and advanced Technology}, \href{http://www.unam.mx/}{UNAM}, Qro, Mex}           
{\href{https://dl.dropboxusercontent.com/u/2115508/Tesis.pdf}{Bubble dynamics subject to novel shockwave: High speed video}\\
summa cum laude, top 3 best GPA 2011, 2012, P.L. 08807255
}
%  \entry
%    {since 2009}
%    {Ph.D. {\normalfont candidate in Computer Science}}
%    {DNET/INRIA, LIP/ÉNS de Lyon}
%    {\emph{A Quantified Theory of Social Cohesion.}}
%  \entry
%    {2007–2008}
%    {M.Sc. magna cum laude}
%    {IXXI, École Normale Supérieure de Lyon}
%    {Majoring in Computer Science\\
%    Specialization in Complex Systems}
%  \entry
%    {2006–2007}
%    {B.Sc. magna cum laude}
%    {École Normale Supérieure de Lyon}
%    {Majoring in Computer Science}
%  \entry
%    {2003–2006}
%    {Classes Préparatoires aux Grandes Écoles}
%    {Lycée Fénelon, Lycée Louis le Grand, Paris}
%    {Preparation for national competitive entrance exams to leading French ``grandes écoles'', specializing in mathematics and physics.}
%  \entry
%    {2003}
%    {French Baccalauréat S. with honors}
%    {Lycée Louis le Grand, Paris}
%    {Specialization in mathematics and physics}
\end{entrylist}


\section{experience}

\begin{entrylist}
\entry
{02/15-08/15}
{\href{http://www.dattlas.com}{Dattlas - Kio Networks}}
{Data Scientist Jr} 
{\textbf{Keywords:} Big Data, SAP HANA, Business Intelligence\\
\textbf{Projects:} Televisa - Big Data
}

\entry
{06/14-01/15}
{\href{http://www.prosciana.com}{Prosciana}}
{Director of Technologic development} 
{\textbf{Keywords:} Big Data, Cloud Computing, Internet of Things, Web Services\\
\textbf{Projects:} K13 | Alarmex | TopCar | Ultralam | Moringa | Lehvi | deconb | Britcan
}

\entry
{01/14-06/14}
{\href{http://www.vintalent.com}{Vintalent Solutions}}
{Data miner}
{\textbf{Keywords:} Web Services, Data Mining}

\entry
{01/13-07/13}
{National Autonomous University of Mexico, Campus Juriquilla}
{Teacher assistant}
%{Classical Mechanics, Bachelor,  \textbf{Main Professor:} Ph.D. Miguel de Icaza Herrera\\
 %Electronics, Bachelor, \textbf{Main Professor:} M.Sc. Francisco Fern\'{a}ndez Escobar}
{\textbf{Keywords:} Classical Mechanics, Electronics}

\entry
{%02/13
08/12-07/13}
{G\&C Consultor\'{i}a}
{Statistical programmer}
%{\textbf{Project Manager:} Q.F.B. Magali Aguilar Ort\'{i}z}
{\textbf{Keywords:} Web Services, Statistical Analysis\\
\textbf{Projects:} UAQ Chemistry | UAQ Nutrition | UAQ Engineering | UAQ Psychology 
}


%\entry
%{08/12-12/12}
%{G\&C Consultor\'{i}a}
%{Statistical programmer}
%{\textbf{Project Manager:} M.Sc. Mar\'{i}a de los \'{A}ngeles Escamilla}

%\entry
%{08/11-12/11}
%{G\&C Consultor\'{i}a}
%{Graphic developer}
%{\textbf{Project Manager:} M.Sc. Mar\'{i}a de los \'{A}ngeles Escamilla}
%
%  \entry
%    {02–07 2009}
%    {LIP6/CNRS, Paris}
%    {Research Internship.}
%    {\emph{Visualization of complex networks.}}
%  \entry
%    {06–08 2008}
%    {ISCPIF/CNRS, Paris}
%    {Research Internship.}
%    {\emph{Diffusion in the Blogosphere. Happy Flu.}}
%  \entry
%    {06–08 2007}
%    {LIP6/CNRS, Paris}
%    {Research Internship.}
%    {\emph{Kernels in real world networks.}}
%  \entry
%    {07–08 2005}
%    {\href{http://www.kelkoo.com}{Kelkoo.com}}
%    {Summer job.}
%    {\emph{Creation of a keyword generator for Google Adwords.}}
%  \entry
%    {07–08 2004}
%    {\href{http://www.monsieurprix.com}{MonsieurPrix.com}}
%    {Summer job.}
%    {\emph{Development of an e-commerce product indexation spider.}}
\end{entrylist}


\section{technical skills}
Extensive ability in mathematical modelling, numerical simulations and computer assisted symbolic calculus. 

Analogical electronics abilities. Microcontroller programming and implementation. 

Big Data Analytics using Apache Hadoop and SAP HANA

Embedded Systems: Software and hardware development with Microchip PIC family, Arduino platform, Raspberry Pi and Texas Instrument Launchpad

   Most common productivity tools on Windows, OS X, Linux desktop and Linux servers
   
   Expertise running multiple instances and services in the \href{http://aws.amazon.com/es/}{Amazon Web Services} cloud: EC2, RDS, S3, DynamoDB, EMR, SES
   
  %\href{http://www.mathworks.com/products/matlab/}{\textsc{Matlab.}}       
%Experience: Linear algebra, Fourier analysis, non-linear numerical simulations, numerical methods, statistics, programming. 
%\href{http://www.wolfram.com/mathematica/}{\textsc{Mathematica.}}
%Experience: Statistics, data visualization, functional analysis, differential geometry, complex analysis, linear algebra, calculus, Wavelet analysis and hardware data streaming
%
%\begin{entrylist}
%  \entry
%    {2012}
%    {Who did I forget ?}
%    {\href{http://whodidiforget.com}{whodidiforget.com}}
%    {Guest list recommendation for Facebook events based on friends already attending the event.}
%  \entry
%    {2011}
%    {Fellows}
%    {\href{http://fellows-exp.com}{fellows-exp.com}}
%    {Automatic community detection among Facebook Friends in order to validate the \emph{cohesion} measure, creation of friend lists.}
%  \entry
%    {2008}
%    {Happy Flu}
%    {\href{http://happyflu.com}{happyflu.com}}
%    {Experiment aimed to measure viral spreading of content across the blogosphere.}
%\end{entrylist}
\newpage
\section{extra courses}
\begin{itemize}
\item II Multidisciplinary mathematical Workshop on applications to other sciences,  Mathematics Institute, UNAM, Juriquilla, Quer\'{e}taro, 24 hours, 2014
\item IX Mathematics Summer School, Mathematics Institute, UNAM, Cuernavaca, Morelos. 40 hours, June 2012
\item XXVII  V\'{i}ctor Neumann-Lara  Colloquium in Graph and Combinatorial Theory and its Applications, Tlaxcala, Tlax., 32 hours, March 2012
\item Mathematics Summer School in Quer\'{e}taro, Center for Innovation in Mathematics, Quer\'{e}taro, Qro, 54 hours, June 2011
\end{itemize}

\section{social service}
Research internship in the Shockwave Laboratory in CFATA-UNAM, 520 hrs.

2014 Gustavo Baz Prada award for the most impacting social service


\section{publications}
\begin{itemize}

\item L\'{o}pez-Roa, C., Perez, L.E., Pedroza, J.C., Icaza, M. de, Castano, V.M.: \href{http://dl.dropbox.com/u/2115508/SRH.pdf}{\emph{Mitos y realidades sobre la situaci\'{o}n de los recursos h\'{i}dricos}}, (2010). A.M Newspaper., Section \emph{Ciencia hoy}, April 24, 2010.

\item Perez-Margay, L.E., L\'{o}pez-Roa, C., Pedroza, J.C., Icaza, M. de, Castano, V.M.: \emph{Optimizaci\'{o}n y aprovechamiento de los recursos h\'{i}dricos.} \href{http://tecnologia.fata.unam.mx/sites/tecnologia.fata.unam.mx/files/coloquio/MC05.pdf}{Memorias del V Coloquio en Tecnolog\'{i}a}. p. 207. Universidad Nacional Aut\'{o}noma de M\'{e}xico, (2010). ISBN: 978-607-02-1439-4

\item L\'{o}pez-Roa, C., Arag\'{o}n, J.L.: \emph{Programaci\'{o}n de \'{A}lgebras de Clifford en Mathematica}. \href{http://dl.dropboxusercontent.com/u/2115508/COT5.pdf}{Memorias del sexto coloquio de Tecnolog\'{i}a}. Universidad Nacional Aut\'{o}noma de M\'{e}xico (2012). ISBN: 978-607-02-3655-6

\item L\'{o}pez-Roa, C., Vargas, A.: \emph{Control robusto de biorreactores basado en modos deslizantes.} \href{https://dl.dropboxusercontent.com/u/2115508/REX6CLR.pdf}{Memorias del octavo coloquio de Tecnolog\'{i}a.} Universidad Nacional Aut\'{o}noma de M\'{e}xico (2012). ISBN: 978-607-02-3654-9

\item L\'{o}pez-Roa, C., Santamar\'{i}a-Holek, I.: \emph{An\'{a}lisis din\'{a}mico del oscilador salino}. \href{https://dl.dropboxusercontent.com/u/2115508/REX7.pdf}{Memorias del noveno coloquio de Tecnolog\'{i}a}. p. 105. Universidad Nacional Aut\'{o}noma de M\'{e}xico. (2012). ISBN: 978-607-02-3943-4

%\item C. L\'{o}pez-Roa, A.Vargas,G. Buitr\'{o}n, \href{http://dl.dropbox.com/u/2115508/COT4.5.pdf}{\emph{Implementaci\'{o}n pr\'{a}ctica de un control \'{o}ptimo en biorreactores aerobios}} 
%
%\item C.L\'{o}pez-Roa, A. Vargas, \href{http://dl.dropbox.com/u/2115508/COT4.pdf}{\emph{Observadores de estado para estimar tasas de reacci\'{o}n en biorreactores aerobios}}, 
\end{itemize} 

%
%\printbibsection{article}{article in peer-reviewed journal}
%\begin{refsection}
%  \nocite{*}
%  \printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=subbibliography]
%\end{refsection}
%\begin{refsection}
%  \nocite{*}
%  \printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=subbibliography]
%\end{refsection}
%\printbibsection{misc}{other publications}
%\printbibsection{report}{research reports}

\section{references}
\textbf{Miguel de Icaza Herrera, PhD. }
e-mail:~\href{mailto:icaza@fata.unam.mx}{icaza@fata.unam.mx};\\ Tel:~442-2381160
\begin{itemize}
\item Researcher in  Centro de F\'{i}sica Aplicada y Tecnolog\'{i}a Avanzada, UNAM. 
\item Molecular Engineering in Materials department.
\end{itemize}

\end{document}
